---
title: "Learning Check 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE, fig.width = 6, fig.asp = 0.618)
library(tidyverse)
```

### I can isolate information from a larger dataset

Read the file `person.csv` from the `data/` folder and store the result in an object called `person`.

```{r load_person_data}

```

Create a tibble that satisfies the following conditions. You do not need to assign this tibble to anything.

1. The tibble contains only family and personal names, in that order.
2. The tibble contains only the rows in which family names come *before* the letter `M`.

Your solution should work for tables with more rows than the example data (i.e., you cannot rely on row numbers or select specific names).

```{r two_columns_and_before_m}

```

Create a tibble with a new column `family_name_length` that contains the lengths of each family names. You do not need to assign this tibble to anything.

```{r name_length}

```

Display all the rows `person` (including `family_name_length`), sorted by family name length with the longest name first. You do not need to assign this tibble to anything.

```{r sorted_name_length}

```


### I can create graphical display of data that highlight key features

In the code chunk below, I load `{gapminder}` and store the `gapminder` dataset to your environment with the `data` function.
Note, you may need to install `{gapminder}` in the **Console** if you experience issues.
Follow these best practices prior to doing that: [Use Caution When Installing Packages in RStudio Server](https://hpcsupport.atlassian.net/servicedesk/customer/portal/3/article/562429973)

```{r load_gapminder}
library(gapminder)
data(gapminder)
```

Create a comparative boxplot that displays `pop` for each country that begins with `"U"`.
Be sure to include a title, informative labels, etc. 

```{r u_boxplots}

```

### I can identify and correct common errors and in R programs

In the below code chunk, I attempt to calculate the number of countries along with the mean and standard deviation of life expectancy for each continent since after year 1990.
However, there are a number of errors in this code.

```{r error_code}
gapminder +
  select(continent, lifeExp) +
  filter(year > 1990) +
  group_by(continent) + 
  summarise(n = n()
            mean_lifeExp = mean(lifeExp)
            sd_lifeExp = sd(lifeExp))
```

Fix these error in the code chunk provide below so that you obtain the following information.
You do not need to use `{knitr::kable}` to produce a markdown table - only fix the errors presented in the code.

|continent |   n| mean_lifeExp   | sd_lifeExp|
|:---------|---:|---------------:|----------:|
|Africa    | 208|        53.83978|   9.396397|
|Americas  | 100|        71.68725|   4.990401|
|Asia      | 132|        68.63002|   8.181951|
|Europe    | 120|        76.07362|   3.253181|
|Oceania   |   8|        78.89862|   1.672702|

```{r fix_errors_here}

```


## Attribution

Ideas for the Application were derived from [Greg Wilson](https://third-bit.com/about/)'s RStudio Instructor training.