---
title: "Learning Check 2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE, fig.width = 6, fig.asp = 0.618)
```

### I can import data from a variety of file types

In the `data` folder...

1. timeanddate.com, "diligently research[es] ... holiday dates and information."
I pulled a list of their holidays and observances for the the ten most populated countries in 2020.
In this file, each country is contained within a separate tab. Read in the data that corresponds to holidays and observances *only* for the United States (the "us" tab) as a tibble and store in an R object with a meaningful name.
You must use functions from `{readxl}` to complete this.

```{r chunk_name}

```


2. Data Scientist Alex Cookson compiled data on TV tropes.
A trope is a storytelling device which is a shortcut for describing situations.
For example, an air vent passageway trope is when people are trapped in a room and escape through air vents (["Yippee ki-yay... Mr. Falcon"](https://youtu.be/Mn-P3lnr76s)).
There are two files related to these TV tropes: `shows.txt` and `tropes.txt`.
Read in these two data files as tibbles and store them in separate R objects, each with a meaningful name.

```{r chunk_name}

```

### I can isolate information from a larger dataset

For the `shows.txt` dataset...

1. Find the 10 most used tropes in the shows.
Your final results should display trope and number of times used.
Display the top 10 results in ascending order (smallest counts first).

```{r chunk_name}

```

### I can combine information from multiple sources

1. Create one dataset that appropriately combines the information from the `shows.txt` and `tropes.txt` data files.
You should assign this to an R object to help you with (2).

```{r chunk_name}

```

2. Using your dataset from (1), create a summary table of the descriptions of the 5 most frequently used tropes.
Your final table should include:

- The top 5 tropes,
- How frequently each of the tropes occurs, and
- A description of each trope.

```{r chunk_name}

```

### I can identify if information is presented in a tidy format and restructure information to be in a tidy format

Using the US holidays and observances dataset, 

1. Which individual state(s) has/have the most observed holidays?
Hint, individual state notes are available in the `Details` column.

```{r chunk_name}

```


### I can put character data into a specified order

Using the `gapminder` dataset...

1. Create a comparative boxplot with `lifeExp` on the *x* axis and `contient` on the *y* axis.
However, make sure that the continents are ordered by descending order rather than the default alphabetical ordering.
You must use function(s) from `{forcats}` in your solution.

```{r chunk_name}

```


### I can use regular expression and other string patterns to manipulate text data

Below I load the `stop_words` tibble for you. Note that this is originally from `{tidytext}` by Julia Silge and David Robinson.

```{r}
stop_words <- read_csv("data/dw_data/stop_words.csv")
```

Using the `tropes.txt` data, 

1. Determine which words are the most frequently occurring in the trope descriptions that are not in `stop_words`.

```{r chunk_name}

```


2. Determine which words are the most unique in the trope descriptions that are not in `stop_words`.

```{r chunk_name}

```


### I can use date/time data to extract portions or perform temporal calculations

Using the US holidays and observances dataset, 

1. Create a bar plot to help you determine which month has the most holidays.
Be sure to use effective axis values.

```{r chunk_name}

```


2. Create a bar plot to help you determine which day of the week has the most holidays.
Be sure to use effective axis values.

```{r chunk_name}

```


### I can create tables of numerical summaries that draw attention to important comparisons

Using the US holidays and observances dataset, 

1. Create a summary table of the frequencies of type of holiday and state observances (not federal holidays).
Be sure that this table is human-readable by making it easy to compare the type of holiday between states.

```{r chunk_name}

```


### I can create graphical display of data that highlight key features

Using the US holidays and observances dataset, 

1. Create a bar graph comparing the number of state holidays for only Michigan, Maine, and Illinois.
You must use user-defined colors, informative labels and values, and a title.

```{r chunk_name}

```


### I can identify and correct common errors and in R programs

1. In the below code chunk, I attempt to calculate the number of mammals for each type of non-missing `vore` (and all mammals that have some type of `conversation`) along with the mean and standard deviation for total sleep.
However, there are a number of errors.

```{r}
msleep %>% 
  select(vore, sleep_total) %>% 
  filter(!is.na(conservation), is.na(vore)) %>% 
  group_by(vore) %>% 
  summarise(n = n(),
            mean_sleep = mean(sleep),
            sd_sleep = sd(sleep))

```

Fix these errors so it obtains the desired results.

```{r chunk_name}

```


### I can explore new functions or packages and implement them into analysis

1. Look into the documentations for the [`{skimr}`](https://github.com/ropensci/skimr) package.
Before installing this, remember the recommended workflow [from HPC](https://hpcsupport.atlassian.net/servicedesk/customer/portal/3/article/562429973).
For the `gapminder` dataset, create summaries for each continent.

```{r chunk_name}

```


## Attribution

Ideas for the Application were derived from [Greg Wilson](https://third-bit.com/about/)'s RStudio Instructor training.