---
title: "Learning Check 6"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE, fig.width = 6, fig.asp = 0.618)
```

### I can import data from a variety of file types

1. Read the file `ssb_characters.red` and store the result in a tibble called `ssb_characters`. This data file contains information on playable characters from the Super Smash Bros. Nintendo game series.



### I can create or get data from the web

The `ssb_characters` datafile contains modified information from the table on the Super Smash Bros. fandom site.
This site also contains a table of [non-playable characters](https://supersmashbros.fandom.com/wiki/List_of_Super_Smash_Bros._series_characters#Non-playable_characters).
Scrape only the Character and Universe information from this table and store this file in a subfolder of the `data` folder - this subfolder should be called `web-scrape`.
For example, if your data frame is called `ssb_npc`, you can use `write_csv(ssb_npc, file = "data/web-scrape/ssb_npc.csv")`.



### I can isolate information from a larger dataset

The data files `at_health_facilities.csv` contains a tidy dataset with four columns:

- The `iso3` code of the country that reported the data.
- The `year` for which data was reported.
- The percentage of HIV-positive children born to HIV-positive mothers age 15-17 (``age 15-17``).
- The percentage of HIV-positive children born to HIV-positive mothers age 20-34 (``age 20-34``).

Below, I read in the `at_health_facilities.csv` file and store the result in a tibble called `at_health_facilities`.

```{r load_facilities_data}
at_health_facilities <- read_csv(here::here("data","dw_data","at_health_facilities.csv"))
```

Using these data, answer the following questions:

1. How many countries reported data?



2. What is the difference between the minimum and maximum year with valid data for each country?



3. Which countries reported 100% incidence for at least one year in either age group?



### I can combine information from multiple sources

This data file contains information on playable characters from the Super Smash Bros. Nintendo game series.
I have not played all of the games that these characters come from; however, I do have some personal ratings for a few of them.

|Universe      |Cuteness |Scariness |Replayability | Epicness |
|:-------------|--------:|---------:|-------------:|---------:|
|Banjo/Kazooie |1        |3         |4             |5         |
|DK            |2        |2         |2             |4         |
|Final Fantasy |5        |5         |5             |1         |
|Mario         |3        |4         |1             |3         |
|Zelda         |4        |1         |3             |2         |

Create a tibble that contains my ratings.
This should be done within R (i.e., do not create a csv and read it in).
Assign this tibble to an object called `bradford_rating`.



Combine `bradford_rating` with the information in `ssb_characters`.
Your final output should contain all information from `ssb_characters` with the additional information from `bradford_rating` on the appropriate rows and missing values elsewhere.



### I can identify if information is presented in a tidy format and restructure information to be in a tidy format

The data files `at_health_facilities.csv` contains a tidy dataset with four columns:

- The `iso3` code of the country that reported the data.
- The `year` for which data was reported.
- The percentage of HIV-positive children born to HIV-positive mothers age 15-17 (``age 15-17``).
- The percentage of HIV-positive children born to HIV-positive mothers age 20-34 (``age 20-34``).

Below, I read in the `at_health_facilities.csv` file and store the result in a tibble called `at_health_facilities`.

```{r load_facilities_data}
at_health_facilities <- read_csv(here::here("data","dw_data","at_health_facilities.csv"))
```

Restructure the data so that the columns are as follows:

- The `iso3` code of the country that reported the data.
- The `year` for which data was reported.
- The HIV-positive mothers' `age_group`.
- The `percentage` of HIV-positive children born to HIV-positive mothers.



### I can put character data into a specified order

Using the `ssb_characters` data, the `*_color` columns contain additional information on playable characters from the Super Smash Bros. Nintendo game series.
This additional information is presented in the table below.

|color  |information                      |
|:------|:--------------------------------|
|None   |Starter                          |
|Grey   |Unlockable                       |
|Red    |Unlockable (3DS)/Starter (Wii U) |
|Yellow |Downloadable                     |
|Blue   |Echo Fighter (Downloadable)      |

1. Using the information above, update `ssb_characters` so that these `*_color` columns display the additional details instead of the color. Theses values should be factors in the order provided in the table (not alphabetical).



2. Update columns `SSB64` through `SSBU` so that the values are either `"Not playable"` (currently `"X mark"`) or `"Playable"` (currently `"Checkmark"`).
There should be no other strings in these new value displays and these values should be factors with `"Playable"` as the first level.



### I can use regular expression and other string patterns to manipulate text data

The Grand Rapids City Archives were gifted a volume of police mugshots which span 1928 to 1934.
This book was saved from a trash bin in 1969 when the former City Hall building and police headquarters were being torn down during part of the city's urban renewal project. Below I read in these data.

```{r mugshots, message = FALSE}
mugshots <- read_csv("data/dw_data/mugshot.csv")
```

1. The variable `Married` currently has several inconsistent entries. Correct this variable by creating a new variable (`married_cleaned`) that only contains the four labels of `"divorced"`, `"no"`, `"widowed"`, and `"yes"`. There should only be three missing (`NA`) values in this new variable. You should assign this to an R object to help you with (2).



2. Create a frequency table for the variable `married_cleaned` to verify that your changes worked.



### I can use date/time data to extract portions or perform temporal calculations

The `lubridate::lakers` dataset contains play by play statistics for each of the LA Lakers basketball games during the 2008-2009 season.

1. Create a bar graph on the number of plays (each play is represented by a row) for each month in the dataset. You must use `{lubridate}` functions and have the months labeled effectively.




### I can create tables of numerical summaries that draw attention to important comparisons

The `{ggplot2}` package has a built in dataset called `diamonds` that contains prices and other attributes of almost 54,000 diamonds.
More information about the variables can be found in the help documentation.

Using this dataset, recreate the table below where the values represent the relative frequency of a diamond's clarity given the diamond's cut (i.e., the rows add up to 100%).

|cut       |    I1|   SI2|   SI1|   VS2|   VS1|  VVS2| VVS1|   IF|
|:---------|-----:|-----:|-----:|-----:|-----:|-----:|----:|----:|
|Fair      | 13.04| 28.94| 25.34| 16.21| 10.56|  4.29| 1.06| 0.56|
|Good      |  1.96| 22.03| 31.80| 19.93| 13.21|  5.83| 3.79| 1.45|
|Very Good |  0.70| 17.38| 26.82| 21.45| 14.69| 10.22| 6.53| 2.22|
|Premium   |  1.49| 21.38| 25.92| 24.34| 14.42|  6.31| 4.47| 1.67|
|Ideal     |  0.68| 12.06| 19.87| 23.53| 16.65| 12.09| 9.50| 5.62|



Does there appear to be a relationship between a diamonds cut and clarity?
That is, if you knew a diamonds clarity, do you have an idea of what cut the diamond is?
Use specific details from the table in your explanation.



### I can create graphical display of data that highlight key features

The `{ggplot2}` package has a built in dataset called `diamonds` that contains prices and other attributes of almost 54,000 diamonds.
More information about the variables can be found in the help documentation.

Create a clustered bar graph that displays the same summarizations (i.e., conditional percentages) as DS.1.
The diamond's cut should be across the x-axis with coloring for a diamond's clarity.



### I can combine multiple graphical displays or numerical summaries into an effective data product

Combine the diamond table and graph from above into one figure.



### I can write a function that accomplishes a common analysis task

1. Write a function called `ratio_to_max` that divides each value in a vector by the maximum of that vector.



Do not edit the below chunk as it is to test your function.

```{r function_check}
ratio_to_max(gapminder::gapminder$lifeExp)
```

Your first six values should be:

```
> head(ratio_to_max(gapminder::gapminder$lifeExp))
[1] 0.3486677 0.3672022 0.3873588 0.4118494 0.4368849 0.4653342
```


### I can use functional programming to apply a function to each element in data source

Below I create a tibble that only contains the numeric columns of `gapminder`.

```{r numeric_gm}
numeric_gm <- gapminder::gapminder %>% 
  select_if(is.numeric)
```

1. Use a function from `{purrr}` to apply your function from FP.1 to each of these columns.



### I can implement resampling methods to make conclusions about data

The `msleep` dataset has information on the amount of time mammals sleep. Below I create two subsets: one for the carnivores and one for the herbivores.

```{r group_sleep}
carni <- ggplot2::msleep %>% 
  filter(vore == "carni")

herbi <- ggplot2::msleep %>% 
  filter(vore == "herbi")
```

1. Using `replicate()`, `sample()`, and `map_dbl()`, perform 1,000 bootstrap samples from the `carni` subset and calculate the mean `sleep_total` for each bootstrap sample. Remember to set a seed and store this in an object named `carni_boot`



2. Using `replicate()`, `sample()`, and `map_dbl()`, perform 1,000 bootstrap samples from the `herbi` subset and calculate the mean `sleep_total` for each bootstrap sample. Remember to set a seed and store this in an object named `herbi_boot`



Below I compute the difference in averages for your two bootstraps.

```{r diff_avg}
diff_boots <- bind_cols(carni = carni_boot, herbi = herbi_boot) %>% 
  mutate(diff = carni_boot - herbi_boot)
```

From the original sample, the sample difference in average `total_sleep` between carnivores and herbivores is

```{r samp_diff_avg}
msleep_diff_avg <- ggplot2::msleep %>% 
  filter(vore %in% c("carni", "herbi")) %>% 
  group_by(vore) %>% 
  summarise(avg = mean(sleep_total)) %>% 
  pivot_wider(names_from = vore,
              values_from = avg) %>% 
  mutate(diff = carni - herbi)

msleep_diff_avg
```

3. How many bootstrap average differences (i.e., `diff_boots$diff`) are as extreme or more extreme than the sample difference in average of 0.87 hrs? That is, determine the number of bootstrap difference in averages that are as small as or smaller than -0.87 hours and as large as or larger than 0.87 hours out of the total 1,000 bootstrap samples. Note that this is your bootstrap "p-value". Is there evidence that carnivores and herbivores total sleep time differs, on average?



### I can use common probability distributions to simulate data and explore statistical ideas

Below is a gamma distribution with shape parameters $\alpha = 0.5$ (`shape1`) and $\beta = 0.5$ (`shape2`). With these two parameters, the population has a mean of 1. Note that the gamma distribution can take on values from 0 to $\infty$, but I am focusing between 0 and 8 so that the graph is viewable.

```{r beta_distribution}
ggplot(data = tibble(x = 0:8), aes(x)) +
  stat_function(fun = dgamma, n = 101, args = list(shape = 2, rate = 2)) +
  labs(title = "Gamma(shape = 2, rate = 2) Distribution") +
  theme_bw() + 
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
```

1. Generate 1,000 samples of size 15 from a Gamma(shape = 2, rate = 2) distribution (hint: `rgamma()`). Calculate the mean for each of the 1,000 samples. You should assign this to an R object to help you with (2).



2. Construct a histogram of the 1,000 means. Be sure to adjust your *x* axis so that it ranges from 0 to 8.



3. What is the mean of the distribution of 1,000 means? What is the shape of the 1,000 means compare to the population?



### I can implement regression and tests of significance to analyze research questions

Using the `ggplot2::msleep` dataset,

1. Fit a linear model for the relationship between the response variable `sleep_rem` and explanatory variables `awake`, `brainwt`, and `bodywt`. Display the model fits as a publication-ready table and interpret slope for each explanatory variable in context of this scenario.



### I can use a project-based workflow to organize and run reproducible analyses

1. Create a new R script
2. Save this R script to a folder named `functions` and name this script `helper.R`.
3. In your `helper.R` script, write a function called `summarise_variable` that takes a tibble name and a variable name and calculates the sample size (n), mean, standard deviation, minimum, and maximum. Make sure that you allow users to specify how to handle missing values. You might find [programming with `{dplyr}`](https://dplyr.tidyverse.org/articles/programming.html) helpful.

Do not edit the code chunk below. This is how I will check that you have completed this Learning Target.

```{r helper_check}
source("functions/helper.R")

summarise_variable(ggplot2::msleep, sleep_rem, na.rm = TRUE)
```



### I can identify and correct common errors and in R programs

1. Below is an attempt to us`{purrr}` functions to fit a regress model for each continent in the `gapminder` dataset except there three errors so that it does not run or will produce the incorrect results. Correct these so that the output is the same.

```{r}
gapminder::gapminder %>% 
  group_by(country) %>% 
  nest() %>%
  mutate(lm_obj = map(data, lm(lifeExp ~ pop + year + gdpPercap, data = .)),
         lm_tidy = map(lm_tidy, broom::tidy)) %>%
  ungroup() %>%
  select(continent, lm_tidy) %>%
  unnest(cols = c(lm_tidy)) %>% 
  knitr::kable()
```



### I can explore new functions or packages and implement them into analysis

1. Using the `msleep` dataset, create an animated plot of your choosing using [{gganimate}](https://gganimate.com/).




## Attribution

Ideas for the Application were derived from [Greg Wilson](https://third-bit.com/about/)'s RStudio Instructor training.